Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description

### 2020-12-02 paper/main.tex
Prep for sharing with Simon
add Simons comments

\documentclass[english]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{svg}
\usepackage{caption, booktabs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancyhdr}
% \usepackage[disable]{todonotes}
\usepackage{todonotes}
\usepackage{units}
\usepackage[left=2cm,right=4cm,top=2cm,bottom=2cm]{geometry}
\usepackage[
	colorlinks=true,
	urlcolor=blue,
	linkcolor=green
]{hyperref}
\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\setlength{\headheight}{40pt}
\lhead{\textsc{\scidatalogo}}
\usepackage{natbib}

@@

@@

@@

@@

@@

\subsection{Stimuli}
% AO & AV stimulus name & references
We used the German DVD release \citep{ForrestGumpDVD} of the audio-visual movie
``Forrest Gump'' \citep{ForrestGumpMovie} and its audio-description that was
broadcast as an additional audio track for visually impaired listeners on Swiss
public television \citep{ForrestGumpGermanAD}.
% AV: voice-over
The plot of the movie is already carried by a voice-over of the main character
Forrest Gump.
% AO: additional narrator
In the largely identical audio-description, an additional male narrator
describes essential aspects of the visual scenery when there is no off-screen
voice, dialog, or other relevant auditory content.

@@

\subsection{Naturalistic stimuli annotation}
% todo stimuli were not designed for research purposes
Both natural stimuli were not design to isolate a specific brain area but to
entertain their audiences free from any perceptual or behavioral task.
% fixed stimuli and operationalization
We annotated the temporal structure of the fixed stimuls material to
operationalize the perception of different stimulus features (e.g. the
perception of landmarks and faces) and create GLM contrasts in the subsequent
data analysis.
% AO annotation
For the analysis of the AO data, we extended an publicly available annotation of
speech \citep{haeusler2020speechanno} by further annotating words spoken by the
audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content.
% categories in detail
Nouns were categorized by the verbal clue they provide about the cinematographic
scene's environment (\texttt{geo}, \texttt{geo-room}; \texttt{setting\_new},
\texttt{setting\_old}), its inherent persons (e.g. \texttt{female},
\texttt{male}, \texttt{persons}), a person's body or worn clothes
(\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a scene's
inherent objects (\texttt{object}, \texttt{furniture}).
% why and how of categories 1
Some categories were created to reflect the six stimulus categories used in the
visual localizer experiment (e.g. \texttt{geo}, \texttt{object}).
% why and how of categories 2
Other categories were created to semantically cluster some remaining nouns into
additional categories (e.g. \texttt{fname}, \texttt{furniture})
% problem with hierarchical categories
Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec} comprise
not just words that describe a setting as a whole (e.g. ``in Greenbow'', ``in a
disco'', ``the platoon wades through a rice field''). They also comprise words
that could count as a member of another categories in case the narrator uses
these words to indicate a switch from one setting to another (e.g. ``Jenny as a
teenager'').
% reference to table with rules and examples
A complete overview of all 19 categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules.
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with counts
The resulting counts for the whole stimulus and the eight stimulus segments used
during fMRI scanning can be seen in Table \ref{tab:descr-nouns-counts}.

@@

@@

\subsection{Procedure}
% questionnaire
Participants filled out a questionnaire on their basic demographic information
and familiarity with the movie.
% AO & AV: instructions
Participants were instructed to inhibit physical movements except for
eye-movements, and otherwise to simply ``enjoy the audiobook'' or ``enjoy the
movie'' respectively.
% AO & AV: presentation & instructions
Audio-description and movie segments were presented in chronological order with
four segments in two fMRI sessions. Between sessions, participants left the
scanner for a break with a flexible duration. Structural images were obtained
during the first study on a day different from the fMRI session.

@@

@@

@@

@@

% procedure
Both annotations were split into eight parts corresponding to the eight stimulus
segments.
% AO events
To create regressors for the AO analysis, we used all of the original 19
categories of descriptive nouns except ``\texttt{++}'' (i.e. cues regarding
time).
% pooling
Some categories that were similar but offered only a small amount of counts were
pooled resulting in eleven new categories that served as experimental conditions
(see Table \ref{tab:ao-events}).
% setting beats other category
Events that fell into one of the two setting-related categories
(\texttt{se\_new} or \texttt{se\_old}) but also into another category were
treated as belonging to the setting-related category (e.g. ``Jenny as a
teenager'').
% modeling as boxcar function
Events were were modeled as boxcar function from onset to offset of each word.
% null regressors
If a segment did not contain an event of a category, a null regressor was chosen
for that category in that segment.\todo{wenn ich "null regressor" nehme, darf
ich den ganzen Run, glaube ich, in der 2nd level Analyse gar nicht benutzen?
Hatte, glaube ich, Jeanette Mumford in einem ihren Videos mal gesagt}
% categories taken from movie cut annotation
Five additional categories were created from the annotation of movie cuts and
modeled as impulse events to capture variance of a possibly confounding change
of the soundscape after a cut, and to create contrasts of cross-modal negative
control (see details below).
% nuisance regressors
Lastly, we used continuous bins of information about two auditory features
(left-right difference in volume and root mean square energy) that was averaged
across the length of every movie frame (\unit[40]{ms}) to capture variance
correlating with low-level perceptual processes.
% Reference to table
An explanation and counts of the eleven speech-related event categories, the
five movie cut-related categories, and the two low-level confounds can be found
in Table \ref{tab:ao-events}.

@@

\begin{table*}[t]
    \caption{Overview of events to build the 14 regressors for the analysis of the audio-only (AV) stimulus.
\texttt{fg\_av\_ger\_lr} (left-right difference in [+++???+++] of
consecutive movie frames).\texttt{fg\_av\_ger\_pd} (perceptual differences of
consecutive frames).
\texttt{fg\_av\_ger\_ud} (up-down difference in [+++???+++] of consecutive movie frames). \texttt{fg\_av\_ger\_lrdiff} (left-right volume difference) and \texttt{fg\_av\_ger\_rms} (root mean square volume) represent one event for every movie frame (\unit[40]{ms}).
For description of the two event categories of the audio-description's
narrator (\texttt{se\_new} and \texttt{se\_old}) to build contrast
of negative control see Table \ref{tab:ao-events}.}
\label{tab:av-events}
\footnotesize
\begin{tabular}{lp{3.5cm}lllllllll}
\toprule
\textbf{label} &  \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
\midrule
vse\_new &  change of the camera position to a setting not depicted before & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII \tabularnewline
vse\_old & change of the camera position to a recurring setting & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII \tabularnewline
vlo\_ch & change of the camera position to another locale within the same setting & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII \tabularnewline
vpe\_new & change of the camera position within a locale not depicted before & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII \tabularnewline
% vpe_old has no events in 3. So the indices are shifted
vpe\_old & change of the camera position within a recurring locale & \aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 & \aoVpeoldIII & \aoVpeoldIV & \aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII \tabularnewline
vno\_cut & a continuous frame from the same camera position & \avVnocutAll & \avVnocutI & \avVnocutII & 0 & \avVnocutIII & \avVnocutIV & \avVnocutV & \avVnocutVI & \avVnocutVII \tabularnewline
se\_new & control for AO narrator & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII \tabularnewline
se\_old & control for AO narrator & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII \tabularnewline
fg\_av\_ger\_lr & XYZ & \avFgavgerlrAll & \avFgavgerlrI & \avFgavgerlrII & \avFgavgerlrIII & \avFgavgerlrIV & \avFgavgerlrV & \avFgavgerlrVI & \avFgavgerlrVII & \avFgavgerlrVIII \tabularnewline
fg\_av\_ger\_lrdiff & left-right volume difference & \avFgavgerlrdiffAll & \avFgavgerlrdiffI & \avFgavgerlrdiffII & \avFgavgerlrdiffIII & \avFgavgerlrdiffIV & \avFgavgerlrdiffV & \avFgavgerlrdiffVI & \avFgavgerlrdiffVII & \avFgavgerlrdiffVIII \tabularnewline
fg\_av\_ger\_ml & +++++???+++++ & \avFgavgermlAll & \avFgavgermlI & \avFgavgermlII & \avFgavgermlIII & \avFgavgermlIV & \avFgavgermlV & \avFgavgermlVI & \avFgavgermlVII & \avFgavgermlVIII \tabularnewline
fg\_av\_ger\_pd & +++++???+++++ & \avFgavgerpdAll & \avFgavgerpdI & \avFgavgerpdII & \avFgavgerpdIII & \avFgavgerpdIV & \avFgavgerpdV & \avFgavgerpdVI & \avFgavgerpdVII & \avFgavgerpdVIII \tabularnewline
fg\_av\_ger\_rms & root mean square (loudness) & \avFgavgerrmsAll & \avFgavgerrmsI & \avFgavgerrmsII & \avFgavgerrmsIII & \avFgavgerrmsIV & \avFgavgerrmsV & \avFgavgerrmsVI & \avFgavgerrmsVII & \avFgavgerrmsVIII \tabularnewline
fg\_av\_ger\_ud & +++++???+++++ & \avFgavgerudAll & \avFgavgerudI & \avFgavgerudII & \avFgavgerudIII & \avFgavgerudIV & \avFgavgerudV & \avFgavgerudVI & \avFgavgerudVII & \avFgavgerudVIII \tabularnewline
\end{tabular}
\end{table*}

% reference to figure ``correlation of regressors''
We computed the Pearson coefficients of the regressors across the eight segments
of both naturalistic stimuli. Results demonstrate no to minor correlations (s.
Figure \ref{fig:reg-corr}) which suggest the models should not suffer from low
detection power due to shared variance among regressors.
%
\todo[inline]{sounds meh but don't know how do write it better; results of
    correlations are given here already; maybe the short discussion (cf. very
    beginning of discussion) of these correlation could be put here too which
    will saves space in the main text; but mixing methods/results/discussion is
not absolutely "clean"}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{figures/regressor-corr}
    \caption{Pearson
        correlation coefficients of the regressors used in the analysis of the
        audio-description (blue; see Table \ref{tab:ao-events} for a
        description) and audio-visual movie (red; see Table
        \ref{tab:av-events}).}
    \label{fig:reg-corr}
\end{figure*}

@@

% we have fixed stimuli
Compared to previous studies we did not design the stimulus material and
experimentally controlled conditions for the
purpose of optimal localization performance since we used fixed stimuli.
% 8 + 5 contrasts
We created eight $t$-contrasts for the AO stimulus (see Table
\ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}) to operationalize ``spatial perception'' compared to
``non-spatial'' perception.\todo{big ouff\dots}
% test for robustness
Creating more than just one contrast for the two
fixed stimuli also let us test for/the robustness of our results across varying
ways operationalization.
% contrasts are of different quality
We assumed all contrasts could in principle isolate the PPA. Nevertheless, we
also assumed contrasts would differ in their isolation performance because they
differ in how well the included event categories reflect on average the
preferred stimulus type processed in the PPA.
% selection of the primary contrast
Thus for each stimulus, we chose one ``primary contrast'' for a detailed report
and discussion of the group-level and subject-specific results. Primary
contrasts were chosen based on how well the used categories on average were
assumed to match the preferred stimulus type in balance with the amount of
available data / events.

% AO COPEs: intro
In context of the AO stimulus, the categories \texttt{se\_new} and
\texttt{se\_old} were problematic for three reasons and thus are not included in
the primary contrast:
% sparse auditory, rich visually
(a) they often only vaguely describe a scene (e.g. ``in Greenbow'', ``in a
disco'', ''black and white film recordings'') whereas a picture of the verbally
described scene would be perceptually richer,
% hierarchical categories
(b) they also comprise words that could count as a member of another category in
case the narrator uses these words to indicate a switch from one setting to
another (e.g. ``Jenny as a teenager'')
% soundscapes forestalls narrator
(c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that already cue a change of settings.  cuts but in AO stimulus
% conclusion
Hence, we assumed contrasts that (exclusively) used these two categories would
induce noise and would be less successful in isolating the PPA.
% furniture
We did not use the category ``furniture'' (\texttt{furn}) as a
regressor of interest in any contrasts because nouns in this category were
usually big and heavy. In a serial stream of auditory information, participants
could perceive furniture-related nouns as either a geometry-defining local scene
element or as an isolated object. Hence we did not use this category as
regressor of interest to reduce noise.
% negative control contrasts
Five $t$-contrasts (see Table \ref{tab:ao-contrasts}) we created as negative
controls to test if increased activation in the PPA was correlated with
moments of cuts and therefore possibly correlated with a accompanying change in
the soundscape.

@@

>>>>

\documentclass[english]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{svg}
\usepackage{caption, booktabs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage[disable]{todonotes}
% \usepackage{todonotes}
\usepackage{units}
\usepackage[left=2cm,right=4cm,top=2cm,bottom=2cm]{geometry}
\usepackage[
	colorlinks=true,
	citecolor=black,
  urlcolor=black,
	linkcolor=black
]{hyperref}
\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\setlength{\headheight}{40pt}
\lhead{\textsc{\scidatalogo}}
\usepackage{natbib}

@@

\todo[inline]{Simon als Autor adden}

\todo[inline]{zweiten Satz: PPA ist die Region im ventral stream, die mehr auf
    static landscapes denn Gesichter reagiert. Ansonsten klingt es so, als ob
    PPA unabhängig von der Funktion definiert ist; dritte Satz ist irgendwie
    falsch konstruiert (narrative... audiovisual movie); ``significant increased
    activation in PPA'': PPA a priori durch localizer definiert? Oder ist der
    increase die Definition der PPA; Beschreibungen sind auf der einen seite
    sehr detailliert, aber der Vergleich mit dem localizer wird nicht explizit
erwähnt; Clou der ganzen Geschichte ist doch: Man braucht keinen separaten
Localizer, oder? Das kommt bisher nur bedingt rüber}

@@

\todo[inline]{Den Start finde ich etwas komisch. "Cognitive neuroscientists use"
klingt sehr nach einer aktiven distanzierung}

\todo[inline]{Ich würde am Start definitiv kurz in die funktionelle
    Spezialisierung des visuellen Systems und die Organisation des ventralen
Streams einführen. Die kurze Darstellung der PPA ist dann aber gut}

\todo[inline]{Der Schwung zu Sprache (wobei speech auch erst am Satzende kommt)
ist zu hart, da kommt man als Leser nicht gut mit}

\todo[inline]{ie "Kritik" an bisherigen PPA Studien finde ich insgesamt OK,
wobei nicht ganz klar wird, was genau das schlechte an "conceptualized" ist. Das
löst sich erst am Ende mit der "ecological validity" einigermaßen auf}

\todo[inline]{Aus meiner Sicht könnte die Motivation für die aktuelle Studie
    noch stärker werden. Du nennst zwar einige Schwächen, aber dann geht es sehr
    unvermittelt in Details der Studie. Meine Präferenz ist es eher, nochmal
    ganz klar zu sagen, warum es jetzt diese Studie braucht und was sie zum Feld
beitragen soll}

\todo[inline]{Damit zusammen hängend: Das Konzept der aktuellen Arbeit (place
information aus einem ongoing context zu verwenden) und warum das die Probleme
löst, würde ich auch noch etwas klarer darstellen. Du setzt zu viel voraus}

\todo[inline]{Das "then we analyzed publically available data" ist sehr
verwirrend, da es doch davor auch um StudyForest geht}

@@

\todo[inline]{describe ``localize / isolate'' in other words}

@@

\todo[inline]{as mit dem "already used by" verwirrt eher}

\todo[inline]{Der StudyForest datansatz ist gut und knapp beschrieben. Die
Stimuli im VIS datensatz brauchen aber glaube ich etwas mehr erklärung}

\todo[inline]{Ich würde mal die Frage antizipieren, wie gut passen die
Annotationen zu den VIS Stimuli. Und die müsste meiner Meinung nach doppelt
beantwortet werden. a) Durch genauere Beschreibung von VIS, b) durch genauere
Ausführungen, wie welche Annotation dazu passt}

@@

\subsection{Stimuli}

\todo[inline]{merge Stimuli and ``Procedure'' (s. below)}

% AO & AV stimulus name & references
We used the German DVD release \citep{ForrestGumpDVD} of the audio-visual movie
``Forrest Gump'' \citep{ForrestGumpMovie} and its audio-description that was
broadcast as an additional audio track for visually impaired listeners on Swiss
public television \citep{ForrestGumpGermanAD}.
% AV: voice-over
The plot of the movie is already carried by a voice-over of the main character
Forrest Gump.
% AO: additional narrator
In the largely identical audio-description, an additional male narrator
describes essential aspects of the visual scenery when there is no off-screen
voice, dialog, or other relevant auditory content.

@@

\subsection{Naturalistic stimuli annotation}

\todo[inline]{Bei AV habt ihr cuts und locations benutzt? Cuts können doch auch
zwischen zwei Gesichtern sein?!?}

% todo stimuli were not designed for research purposes
Both natural stimuli were not design to isolate a specific brain area but to
entertain their audiences free from any perceptual or behavioral task.
% fixed stimuli and operationalization
We annotated the temporal structure of the fixed stimuls material to
operationalize the perception of different stimulus features (e.g. the
perception of landmarks and faces) and create GLM contrasts in the subsequent
data analysis.
% AO annotation
For the analysis of the AO data, we extended an publicly available annotation of
speech \citep{haeusler2020speechanno} by further annotating words spoken by the
audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content.
% categories in detail
Nouns were categorized by the verbal clue they provide about the cinematographic
scene's environment (\texttt{geo}, \texttt{geo-room}; \texttt{setting\_new},
\texttt{setting\_old}), its inherent persons (e.g. \texttt{female},
\texttt{male}, \texttt{persons}), a person's body or worn clothes
(\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a scene's
inherent objects (\texttt{object}, \texttt{furniture}).
% why and how of categories 1
Some categories were created to reflect the six stimulus categories used in the
visual localizer experiment (e.g. \texttt{geo}, \texttt{object}).
% why and how of categories 2
Other categories were created to semantically cluster some remaining nouns into
additional categories (e.g. \texttt{fname}, \texttt{furniture})
% problem with hierarchical categories
Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec} comprise
not just words that describe a setting as a whole (e.g. ``in Greenbow'', ``in a
disco'', ``the platoon wades through a rice field''). They also comprise words
that could count as a member of another categories in case the narrator uses
these words to indicate a switch from one setting to another (e.g. ``Jenny as a
teenager'').
% reference to table with rules and examples
A complete overview of all 19 categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules.
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with counts
The resulting counts for the whole stimulus and the eight stimulus segments used
during fMRI scanning can be seen in Table \ref{tab:descr-nouns-counts}.

@@

\todo[inline]{Table 2 ist relativ kryptisch bzw für jemanden, der sich zum
    ersten Mal damit auseinander setzt kaum zu verstehen. Auch ist der Bezug zum
GLM unklar, d.h., was davon wird verwendet und was verbirgt sich dahinter}

\todo[inline]{Ich merke das mal hier an: Die Tables stehen an ganz merkwürdigen
Positionen, das passt nicht zum Text und verwirrt ungemein}

@@

\subsection{Procedure}

\todo[inline]{Procedure (2.4.) ist nicht zwingend nötig bzw nicht als
separater Abschnitt}

% questionnaire
Participants filled out a questionnaire on their basic demographic information
and familiarity with the movie.
% AO & AV: instructions
Participants were instructed to inhibit physical movements except for
eye-movements, and otherwise to simply ``enjoy the audiobook'' or ``enjoy the
movie'' respectively.
% AO & AV: presentation & instructions
Audio-description and movie segments were presented in chronological order with
four segments in two fMRI sessions. Between sessions, participants left the
scanner for a break with a flexible duration. Structural images were obtained
during the first study on a day different from the fMRI session.

@@

\todo[inline]{shorten this subsection a lot}

@@

\todo[inline]{Ich würde abschnitt 2.8 teilen (in die regressors, die dann mit
der beschreibung der annotation kombinieren, und die eigentliche statistik)}

\todo[inline]{Ich weiss nicht, ob es die etwas wild zwischendrin stehenden
    tables waren, die oft komplizierten Beschreibungen, die Länge des
    Abschnittes, oder alles zusammen, aber ich habe mich mit 2.8 extrem schwer
    getan. Bitte lass den Reviewer nicht mit dem selben Gefühl rausgehen. Gut
strukturiert, einfach und klar ist immer vom Vorteil}

@@

\todo[inline]{Das mit den "five additional categories" habe ich nicht
    verstanden. Überhaupt finde ich die ganze Beschreibung relativ schwer zu
durchdrungen, und ich glaube damit werde ich nicht alleine sein.}

\todo[inline]{Gab es ein separates null-event für jeden zeitraum zwischen zwei
annotierten events oder war das ein regressor der immer wieder kam?}

\todo[inline]{Ich würde vorschlagen, dass Du Dich auf die Regressoren / Events
    konzentrierst, die hier wichtig sind, um die Komplexität zu reduzieren. Die
    aber dafür besser erklären (was heißt "unfamilar perspective"? Ab wann ist
ein setting "familiar"?}

@@

% procedure
Both annotations were split into eight parts corresponding to the eight stimulus
segments.
% AO events
To create regressors for the AO analysis, we used all of the original 19
categories of descriptive nouns except ``\texttt{++}'' (i.e. cues regarding
time).
% pooling
Some categories that were similar but offered only a small amount of counts were
pooled resulting in eleven new categories that served as experimental conditions
(see Table \ref{tab:ao-events}).
% setting beats other category
Events that fell into one of the two setting-related categories
(\texttt{se\_new} or \texttt{se\_old}) but also into another category were
treated as belonging to the setting-related category (e.g. ``Jenny as a
teenager'').
% modeling as boxcar function
Events were were modeled as boxcar function from onset to offset of each word.
% null regressors
If a segment did not contain an event of a category, a null regressor was chosen
for that category in that segment.\todo{wenn ich "null regressor" nehme, darf
ich den ganzen Run, glaube ich, in der 2nd level Analyse gar nicht benutzen?
Hatte, glaube ich, Jeanette Mumford in einem ihren Videos mal gesagt}
% categories taken from movie cut annotation
Five additional categories were created from the annotation of movie cuts and
modeled as impulse events to capture variance of a possibly confounding change
of the soundscape after a cut, and to create contrasts of cross-modal negative
control (see details below).
% nuisance regressors
\todo[inline]{"Continuous bins lasting 40ms" ?!?}
%
Lastly, we used continuous bins of information about two auditory features
(left-right difference in volume and root mean square energy) that was averaged
across the length of every movie frame (\unit[40]{ms}) to capture variance
correlating with low-level perceptual processes.
% Reference to table
An explanation and counts of the eleven speech-related event categories, the
five movie cut-related categories, and the two low-level confounds can be found
in Table \ref{tab:ao-events}.

@@

    \caption{Overview of events to build the 14 regressors for the analysis of
        the audio-visual (AV) stimulus.
        \texttt{fg\_av\_ger\_pd} (perceptual differences of consecutive frames),
        \texttt{fg\_av\_ger\_ml} (mean luminance of a frame),
        \texttt{fg\_av\_ger\_lr} (difference in mean luminance of left and
        right half),
        \texttt{fg\_av\_ger\_ud} (difference in mean luminance of upper and
        lower half),
        \texttt{fg\_av\_ger\_lrdiff} (left-right volume difference), and
        \texttt{fg\_av\_ger\_rms} (root mean square volume) represent one event
        for every movie frame (\unit[40]{ms}).
        For description of the two event categories of the audio-description's
        narrator (\texttt{se\_new} and \texttt{se\_old}) to build contrast
        of negative control see Table \ref{tab:ao-events}.}
\label{tab:av-events}
vse\_new &  change of the camera position to a setting not depicted before & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII \tabularnewline
vse\_old & change of the camera position to a recurring setting & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII \tabularnewline
vlo\_ch & change of the camera position to another locale within the same setting & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII \tabularnewline
vpe\_new & change of the camera position within a locale not depicted before & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII \tabularnewline
vpe\_old & change of the camera position within a recurring locale & \aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 & \aoVpeoldIII & \aoVpeoldIV & \aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII \tabularnewline
vno\_cut & a continuous frame from the same camera position & \avVnocutAll & \avVnocutI & \avVnocutII & 0 & \avVnocutIII & \avVnocutIV & \avVnocutV & \avVnocutVI & \avVnocutVII \tabularnewline
se\_new & control for AO narrator & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII \tabularnewline
se\_old & control for AO narrator & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII \tabularnewline
fg\_av\_ger\_lr & left-right luminance difference & \avFgavgerlrAll & \avFgavgerlrI & \avFgavgerlrII & \avFgavgerlrIII & \avFgavgerlrIV & \avFgavgerlrV & \avFgavgerlrVI & \avFgavgerlrVII & \avFgavgerlrVIII \tabularnewline
fg\_av\_ger\_lrdiff & left-right volume difference & \avFgavgerlrdiffAll & \avFgavgerlrdiffI & \avFgavgerlrdiffII & \avFgavgerlrdiffIII & \avFgavgerlrdiffIV & \avFgavgerlrdiffV & \avFgavgerlrdiffVI & \avFgavgerlrdiffVII & \avFgavgerlrdiffVIII \tabularnewline
fg\_av\_ger\_ml & mean luminance & \avFgavgermlAll & \avFgavgermlI & \avFgavgermlII & \avFgavgermlIII & \avFgavgermlIV & \avFgavgermlV & \avFgavgermlVI & \avFgavgermlVII & \avFgavgermlVIII \tabularnewline
fg\_av\_ger\_pd & perceptual difference & \avFgavgerpdAll & \avFgavgerpdI & \avFgavgerpdII & \avFgavgerpdIII & \avFgavgerpdIV & \avFgavgerpdV & \avFgavgerpdVI & \avFgavgerpdVII & \avFgavgerpdVIII \tabularnewline
fg\_av\_ger\_rms & root mean square (loudness) & \avFgavgerrmsAll & \avFgavgerrmsI & \avFgavgerrmsII & \avFgavgerrmsIII & \avFgavgerrmsIV & \avFgavgerrmsV & \avFgavgerrmsVI & \avFgavgerrmsVII & \avFgavgerrmsVIII \tabularnewline
fg\_av\_ger\_ud & upper-lower luminance difference & \avFgavgerudAll & \avFgavgerudI & \avFgavgerudII & \avFgavgerudIII & \avFgavgerudIV & \avFgavgerudV & \avFgavgerudVI & \avFgavgerudVII & \avFgavgerudVIII \tabularnewline

%
\todo[inline]{Die Abkürzungen in Figure 1: Da steigt keiner hinter}

\todo[inline]{Habe jetzt lange darüber gebrütet: Es gibt also kaum eine
Korrelation zwischen AO und AV?; Also, außer bei fg\_av\_ger\_lr\_diff (wobei da keiner weiss, was das bedeutet)}
% reference to figure ``correlation of regressors''
We computed the Pearson coefficients of the regressors across the eight segments
of both naturalistic stimuli. Results demonstrate no to minor correlations (s.
Figure \ref{fig:reg-corr}) which suggest the models should not suffer from low
detection power due to shared variance among regressors.
%
\todo[inline]{sounds meh but don't know how do write it better; results of
    correlations are given here already; maybe the short discussion (cf. very
    beginning of discussion) of these correlation could be put here too which
    will saves space in the main text; but mixing methods/results/discussion is
not absolutely "clean"}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{figures/regressor-corr}
    \caption{Pearson
        correlation coefficients  of the regressors used in the analysis of the
        audio-description (blue; see Table \ref{tab:ao-events} for a
        description) and audio-visual movie (red; see Table
        \ref{tab:av-events}) rounded to the nearest tenth.
        The correlation
        between the two stimuli's root mean square loudness and between their
        left-right difference in loudness yielded the highest correlation
        values (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635
        \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749).}
    \label{fig:reg-corr}
\end{figure*}

@@

%
 \todo[inline]{Das mit den 8 kontrasten und 5 kontrasten habe ich nicht intuitiv
 durchblickt. Was wurde da gegen was kontrastiert?}
% we have fixed stimuli
Compared to previous studies we did not design the stimulus material and
experimentally controlled conditions for the
purpose of optimal localization performance since we used fixed stimuli.
% 8 + 5 contrasts
We created eight $t$-contrasts for the AO stimulus (see Table
\ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}) to operationalize ``spatial perception'' compared to
``non-spatial'' perception.\todo{big ouff\dots}
% test for robustness
Creating more than just one contrast for the two
fixed stimuli also let us test for/the robustness of our results across varying
ways operationalization.
% contrasts are of different quality
We assumed all contrasts could in principle isolate the PPA. Nevertheless, we
also assumed contrasts would differ in their isolation performance because they
differ in how well the included event categories reflect on average the
preferred stimulus type processed in the PPA.
% selection of the primary contrast
Thus for each stimulus, we chose one ``primary contrast'' for a detailed report
and discussion of the group-level and subject-specific results. Primary
contrasts were chosen based on how well the used categories on average were
assumed to match the preferred stimulus type in balance with the amount of
available data / events.

% AO COPEs: intro
In context of the AO stimulus, the categories \texttt{se\_new} and
\texttt{se\_old} were problematic for three reasons and thus are not included in
the primary contrast:
% sparse auditory, rich visually
(a) they often only vaguely describe a scene (e.g. ``in Greenbow'', ``in a
disco'', ''black and white film recordings'') whereas a picture of the verbally
described scene would be perceptually richer,
% hierarchical categories
(b) they also comprise words that could count as a member of another category in
case the narrator uses these words to indicate a switch from one setting to
another (e.g. ``Jenny as a teenager'')
% soundscapes forestalls narrator
(c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that already cue a change of settings.
% conclusion
Hence, we assumed contrasts that (exclusively) used these two categories would
induce noise and would be less successful in isolating the PPA.
% furniture
We did not use the category ``furniture'' (\texttt{furn}) as a
regressor of interest in any contrasts because nouns in this category were
usually big and heavy. In a serial stream of auditory information, participants
could perceive furniture-related nouns as either a geometry-defining local scene
element or as an isolated object. Hence we did not use this category as
regressor of interest to reduce noise.
% negative control contrasts
Five $t$-contrasts (see Table \ref{tab:ao-contrasts}) we created as negative
controls to test if increased activation in the PPA was correlated with
moments of cuts and therefore possibly correlated with a accompanying change in
the soundscape.

@@

\todo[inline]{give reference to Neurovault.com}

\todo[inline]{- Bitte sauber differenzieren zwischen "Lokalisation der PPA" und
    "Antwortverhalten einer vorab definierten PPA". Ich habe den Eindruck, dass
Du oft das erste machst es aber als das zweite beschreibst}

\todo[inline]{Der vergleich mit VIS kommt bestenfalls en passant, VIS selber
wird gar nicht berichtet wäre aber wichtig zum andocken an die Literatur}

\todo[inline]{Es ist zwar hier nicht der Fokus, aber ich würde sehr darauf
wetten, dass Reviewer danach fragen: Wie sieht es im vergleich dazu mit Faces
aus?}

\todo[inline]{Figure 2 und 3: ich würde da wahrscheinlich weiter rein zoomen um
genauer den visuellen Kortex zu zeigen. Vor allem aber muss man sagen, dass bei
FFA/PPA etc eigentlich flatmaps bzw inflated brains, also surface-darstellungen
standard sind}
